Supermassive black holes and their host spheroids \\ I. Galaxy vivisection

### 2015-11-20 papers/data_paper/arxiv/datapaper.tex
victory2

%\and

%\author{A. W. Graham\altaffilmark{1}}
%\affil{Centre for Astrophysics and Supercomputing, Swinburne University of Technology, Hawthorn, Victoria 3122, Australia.}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

%\altaffiltext{1}{Visiting Astronomer, Cerro Tololo Inter-American Observatory.
%CTIO is operated by AURA, Inc.\ under contract to the National Science
%Foundation.}
%\altaffiltext{2}{Society of Fellows, Harvard University.}
%\altaffiltext{3}{present address: Center for Astrophysics,
%    60 Garden Street, Cambridge, MA 02138}
%\altaffiltext{4}{Visiting Programmer, Space Telescope Science Institute}
%\altaffiltext{5}{Patron, Alonso's Bar and Grill}

@@

Supermassive black holes and their host spheroids\footnote{\bf By the term ``spheroid'' 

@@

{\bf (see also \citealt{kormendygebhardt2001,erwingadotti2012})}.

@@

\section{Data}
\label{sec:data}
%\subsection{Initial sample}
Our initial galaxy sample (see Table \ref{tab:sample}) consists of 75 objects for which a dynamical detection of the black hole mass 
had been reported in the literature at the time we started this project, 
and for which at least one $3.6~\rm \mu m$ \emph{Spitzer}/IRAC\footnote{IRAC is the InfraRed Array Camera onboard the \emph{Spitzer} Space Telescope.} 
observation was publicy available.
Black hole masses were drawn from the catalog of \citet{grahamscott2013} for 70 galaxies,
from \citet{rusli2013bhmassesDM} for 4 galaxies and from \citet{greenhill2003} for 1 galaxy. 
As explained in Section \ref{sec:res}, 
this initial sample was ultimately reduced to 66 galaxies for which useful spheroid parameters could be obtained.

%\clearpage
\input{table_sample.tex}
%\noindent
%\input{table_observations.tex}

\subsection{\emph{Spitzer}/IRAC observations}
\subsubsection{Data acquisition}
For each of our 75 galaxies, we downloaded from the 
Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs). 
Each AOR is an individual Spitzer observation sequence, and
includes a number of data frames (the individual exposures) and the calibration data.
The data frames were selected to be %``enhanced Level 1 products'', or
corrected Basic Calibrated Data (cBCD), produced by the IRAC Level 1 pipeline. 
This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
and performs dark subtraction, flatfielding correction and flux calibration (into units of $\rm MJy~sr^{-1}$). 
The final product (the BCD) is a flux-calibrated image which has had all the well-understood instrumental signatures removed.
BCD frames are further processed through an ``artifact correction'' pipeline 
that mitigates the commonly found artifacts of stray light, saturation, ``muxbleed'' and column pulldown\footnote{Stray light 
includes scattered light from stars outside the array location as well as filter ghosts from bright stars. 
Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
It appears as a decaying trail of pixels, repeating every fourth column.
``Column pulldown'' is caused by a bright pixel that triggers a bias shift within its respective column, 
creating a lower background value throughout the entire column than in the surrounding columns.}.
After the artifact correction has been applied, the BCD becomes a cBCD.

@@

\subsubsection{Sky subtraction}
Sky subtraction was performed manually on the image mosaics using the tasks {\tt marksky} and {\tt skyfit} 
of the IRAF\footnote{IRAF is the Image Reduction and Analysis Facility, 
distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} 
package GALPHOT\footnote{GALPHOT was developed in the IRAF - STSDAS environment mainly by 
W. Freudling, J. Salzer, and M. P. Haynes \citep{haynes1999galphot}.}.
The task {\tt skyfit} also provided an estimate of the sky root mean square ($RMS_{\rm sky}$).
%sky value also checked with Galfit

@@

\subsubsection{1D PSF}
A universal\footnote{\bf Across all mosaics, the variation of the Moffat $FWHM$ is $\pm 0''.1$, 
and the variation of the Moffat $\beta$ is $\pm 2.0$.
The use of a universal PSF is justified for the following reasons: 
\emph{i}) the PSF-convolution is more sensitive to the value of the $FWHM$ than $\beta$, 
i.e. having a 50\% variation in $\beta$ is not an issue as long as the variation in $FWHM$ is small;
\emph{ii}) the use of a non-signal-to-noise-weighted fitting scheme minimizes biases from a non-accurate PSF description;
\emph{iii}) not all mosaics have enough stars suitable for the PSF characterization: 
rather than having an individual PSF for each mosaic (which would have been based on only 1-2 stars for some mosaics), 
we preferred the use of a universal PSF.}, 
average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \cite{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained 
$(\alpha, \beta) = (2''.38, 4.39)$.

@@

\section{Analysis}
\label{sec:anal}
\subsection{Isophotal analysis}
We performed an isophotal analysis of our galaxies using the IRAF task {\tt ellipse} \citep{taskellipse}, 
which fits elliptical isophotes to galaxy images.
The center of the isophotes was held fixed, while the ellipticity ($\epsilon$), the position angle ($P.A.$),  
and the amplitude of the fourth harmonic\footnote{The amplitude of the fourth harmonic deviations from perfect ellipses 
($B4$) parameterizes the diskyness ($B4>0$) or boxyness ($B4<0$) of the isophotes.} ($B4$) were allowed to vary with radius.
The step in semi-major axis length between successive ellipses was first set to increase linearly, 
and then geometrically in our second run\footnote{In the case of linear steps, 
the semi-major axis length for the next ellipse was calculated by adding $1$ pixel to the current length.
In the case of geometric steps, the semi-major axis length for the next ellipse 
was calculated as $1.1$ times the current length.}.
As a result, for each galaxy we produced respectively a ``linearly sampled'' and a ``logarithmically sampled'' 
surface brightness profile along the major-axis. 
Major-axis surface brightness profiles were additionally converted into the equivalent-axis,
i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$), 
equivalent to the circularized radius.
This resulted in 4 profiles per galaxy.
Isophotes corresponding to an intensity less than 
three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$) were ignored.
Some surface brightness profiles were truncated at our discretion before the $3 \times RMS_{\rm sky}$ limit, 
according to specific technical reasons (e.g.~contamination from light of a neighboring galaxy, 
disturbed morphology in the galaxy outskirts, etc.). 
{\bf In particular, we did not attempt to fit bends or truncations of large-scale disks 
(e.g.~\citealt{erwin2005,erwin2008,erwin2012,gutierrez2011,comeron2012,munozmateos2013,kim2014}) 
but instead truncated the surface brightness profiles before the occurrence of such features. }
Individual cases are discussed in Section \ref{sec:indgal}.

@@

\subsection{1D fitting routine}
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
This software can fit an observed surface brightness profile with any linear combination of 
a set of analytical functions (S\'ersic, exponential, Gaussian, Moffat, Ferrer, symmetric Gaussian ring etc. 
see Appendix \ref{sec:app1} for a description of the analytical form of these profiles).
At each iteration, 
the model is numerically convolved with a Moffat filter, to account for PSF effects, 
and then matched to the data.
The minimization routine is based on the Levenberg-Marquardt algorithm.
During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
surface brightness profile, 
although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
The all too often over-looked flaw with (signal-to-noise)-based weighting schemes 
is that they immediately become biased weighting schemes when additional components are present but not modelled.
For example, fitting only a S\'ersic model to what is actually a nucleated elliptical galaxy immediately voids 
a (signal-to-noise)-based weighting scheme 
and results in S\'ersic parameters which describe the spheroid less accurately than had no (signal-to-noise)-weighting been used.
While we have paid careful attention to the components in each galaxy, 
this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
{\bf Over-looked partially depleted cores, or an incorrect PSF, can of course also result in (signal-to-noise)-weighted fitting schemes 
performing poorly because of the emphasis they place on matching the model to the inner data. }

@@

{\bf As stressed in Section \ref{sec:int}, our investigation is primarily focused on the central spheroidal components 

@@

We modeled spheroids/bulges with a S\'ersic profile, without attempting to distinguish between classical and pseudo-bulges. } \\

@@

{\bf \cite{savorgnangraham2015ellicular} extensively discuss the topic of galaxies with intermediate-scale disks 

@@

which makes these galaxies falsely appear as extreme outliers in the (black hole mass)-(spheroid stellar mass) diagram. } \\

@@

{\bf As noted, we were able to successfully fit bars with a Ferrer function 

@@

in a few cases, with a Ferrer function\footnote{\bf One advantage of choosing a Ferrer function over a S\'ersic profile 

@@

as is commonly found for bars in ``early-type spiral'' galaxies \citep{gadottidesouza2006}. } \\

@@

{\bf (\citealt{wadadekar1999,ravindranath2001,peng2002} and \citealt{gadotti2008} discuss the importance of fitting nuclear components)}. \\

@@

\subsection{2D fits}
\label{sec:2d}
Two-dimensional decompositions were carried out using the software \textsc{Imfit} \citep{imfit}.
For each galaxy, we built a 2D model that was consistent with the corresponding 1D model in terms of number and type of components. 
{\bf The only difference between our 1D and 2D models pertains to the description of bars: 
because the Ferrer profile is not made available in \textsc{Imfit},
bars were fit with a 2D Gaussian function. } \\
The 2D decomposition of NGC 2974 is presented in Figure \ref{fig:n29742d}. 
The galaxy was modeled with a S\'ersic bulge, an exponential disk and a Gaussian bar.
The nuclear component was masked and the ring was not 
modeled\footnote{We built the 2D model first including and then omitting a gaussian ring component, 
but both models converged to the same solution, i.e.~the fit ``ignored'' the presence of the faint ring. 
This did not happen in the 1D decomposition because of the different weighting scheme used by the fitting routines.}. 
Our best-fit 2D model returns a bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 10.5~\rm arcsec$, 
a bulge S\'ersic index $n_{\rm sph} = 1.3$ and a $3.6~\rm \mu m$ bulge apparent magnitude $m_{\rm sph} = 8.39~\rm mag$, 
in fairly good agreement with our 1D decomposition. 
Fits and descriptions for the other galaxies are available online.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{n2974_imgmsk.eps}
\includegraphics[width=\columnwidth]{n2974_unsharp.eps}
\includegraphics[width=\columnwidth]{n2974_model.eps}
\includegraphics[width=\columnwidth]{n2974_resid.eps}
\caption{Image of the galaxy NGC 2974 with its mask (top panel, {\bf on a logarithmic scale}), 
unsharp mask (second panel, {\bf on a linear scale}), 
best-fit 2D model (third panel, {\bf on a logarithmic scale}), 
and residual image after the subtraction of the 2D model (bottom panel, {\bf on a linear scale; 
the residual patterns correspond to differences between the data and the model of less than 6\%}).
The lefthand side of the mosaic allowed an accurate determination of the sky background level.}
\label{fig:n29742d}
\end{center}
\end{figure}

@@

\subsection{1D versus 2D decompositions}
Here we explore how 1D and 2D decompositions compare with each other. 
Readers not interested in our practical knowledge, 
having dealt with 1D and 2D techniques of galaxy modeling at the same time, can skip to Section \ref{sec:err}. 
We summarize our experience in the following points:
\begin{itemize}
\item A visual inspection of galaxy images and their unsharp masks is often not sufficient to accurately identify all of a galaxy's components. 
Weak bars and some embedded disks can easily be missed. 
Other (inclined) embedded disks can be confused with large-scale disks.
In this regards, the 1D isophotal analysis is extremely helpful. 
Local minima/maxima or abrupt changes in the ellipticity, position angle and fourth harmonic profiles contain precious information 
about a galaxy's constituents.
\item The ellipticity and position angle of triaxial spheroids can vary with radius.
The analytic functions used by 2D decomposition codes to fit galaxy components have fixed ellipticity and position angle, 
thus they cannot account for these radial gradients. 
This problem is overcome with 1D decomposition techniques 
{\bf because the ellipticity, and additionally the deviations from elliptical isophotes, 
are efficiently included in the equivalent-axis fit (see the Appendix of \citealt{ciambur2015})}.
\item The interpretation of the residual surface brightness profile is often crucial to identify the optimal decomposition for a galaxy. 
In our experience, we found that interpreting 1D residuals was easier and more productive than 2D residuals.
\end{itemize}
Although we attempted 2D modeling for the 72 galaxies in our sample, 
more than half of the 2D decompositions were not successful or did not converge to a meaningful solution. 
This should serve as a tip to users of 2D fitting codes. 
When physically meaningful spheroid parameters are required, 
the output may not be reliable and should be inspected.
For the 31 galaxies that had successful 2D decompositions, 
we compare with their 1D parameters in Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}.
The agreement between 1D and 2D effective radii and magnitudes is remarkable, 
whereas a larger amount of scatter in the S\'ersic indices can be caused by the fact that 
2D measurements do not exactly correspond to 1D equivalent-axis measurements. 
No systematic effects are observed in any of these three plots, 
which indicates that 1D and 2D techniques of galaxy modeling -- when performed on the same galaxy -- 
can give consistent results. \\
In conclusion, since we found that the best-fit parameters do not depend on the decomposition method (1D or 2D) used, 
and given that we obtained more successful 1D decompositions than 2D, 
we will base our analysis on the results from the 1D fits.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{comparison_n.eps} 
\caption{2D measurements of the spheroid S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
The dashed line displays the 1:1 relation.
{\bf The four most obvious outliers are NGC 821, NGC 3377, NGC 4945, and NGC 5576. 
Their individual cases are discussed in the Appendix. }}
\label{fig:n1d2d}
\end{center}
\end{figure}

@@

{\bf When we identified, 
but were not able to model a galaxy sub-component with the same accuracy dedicated to the other components}.

@@

\subsubsection{Uncertainties on $n_{\rm sph}$}
In Figure \ref{fig:compn}, for 58 galaxies, 
we compare the measurements of the spheroid S\'ersic index obtained by different authors 
with those obtained by us. 
For each galaxy, we computed the average value $\langle \log(n_{\rm sph}) \rangle$ of the available measurements, 
and we plot it against the scatter of the individual measurements around each spheroid's $\langle \log(n_{\rm sph}) \rangle$.
The measurements are heterogeneous, 
in the sense that they were obtained from 1D or 2D decompositions of data in different wavelengths, 
and they refer either to the major-axis, the equivalent-axis or some 2D average.
In Figure \ref{fig:compn}, the black histogram shows the distribution of the scatter around $\langle \log(n_{\rm sph}) \rangle$ 
for our measurements. 
38\% of this distribution lie within $-\sigma_1^- = -0.08~\rm dex$ and $+\sigma_1^+ = +0.06~\rm dex$, 
78\% lie within $-\sigma_2^- = -0.21~\rm dex$ and $+\sigma_2^+ = +0.17~\rm dex$,
and 92\% lie within $-\sigma_3^- = -0.25~\rm dex$ and $+\sigma_3^+ = +0.25~\rm dex$. 
We elect to use $\pm \sigma_1^\pm$, $\pm \sigma_2^\pm$ and $\pm \sigma_3^\pm$ as $1\sigma$ uncertainties 
for our measurements of $\log(n_{\rm sph})$ obtained from ``grade 1'', ``grade 2'' and ``grade 3'' fits, respectively. 
{\bf This means that, if the fit to a galaxy was classified as ``grade 1'', 
the (logarithmic) value of the spheroid S\'ersic index $\tilde{n}_{\rm sph}$ and associated uncertainties would be 
$\log(\tilde{n}_{\rm sph})^{+\sigma_1^+}_{-\sigma_1^-} = \log(\tilde{n}_{\rm sph})^{+0.06}_{-0.08}$; 
if the fit to that galaxy was classified as ``grade 2'', 
then one would have $\log(\tilde{n}_{\rm sph})^{+\sigma_2^+}_{-\sigma_2^-} = \log(\tilde{n}_{\rm sph})^{+0.17}_{-0.21}$, 
and so on.  }

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{m104_1Dfit.eps}
  \caption{M104: 
  A lenticular/spiral galaxy with a partially depleted core \citep{jardel2011}. 
  The data within the innermost $6''.1$ are excluded from the fit, 
  and the most obvious elongated feature of this galaxy is modeled with a Ferrer function. 
  The ellipticity profile indicates that the disk is of intermediate-scale 
  {\bf (for a thorough analysis of this galaxy, see \citealt{gadottisanchezjanssen2012})}.
  }
  \end{center}
  \end{figure}

>>>>

@@

Supermassive black holes and their host spheroids\footnote{By the term ``spheroid'' 

@@

(see also \citealt{kormendygebhardt2001,erwingadotti2012}).

@@

\section{Data}
\label{sec:data}
Our initial galaxy sample (see Table \ref{tab:sample}) consists of 75 objects for which a dynamical detection of the black hole mass 
had been reported in the literature at the time we started this project, 
and for which at least one $3.6~\rm \mu m$ \emph{Spitzer}/IRAC\footnote{IRAC is the InfraRed Array Camera onboard the \emph{Spitzer} Space Telescope.} 
observation was publicy available.
Black hole masses were drawn from the catalog of \citet{grahamscott2013} for 70 galaxies,
from \citet{rusli2013bhmassesDM} for 4 galaxies and from \citet{greenhill2003} for 1 galaxy. 
As explained in Section \ref{sec:res}, 
this initial sample was ultimately reduced to 66 galaxies for which useful spheroid parameters could be obtained.

\input{table_sample.tex}

\subsection{\emph{Spitzer}/IRAC observations}
\subsubsection{Data acquisition}
For each of our 75 galaxies, we downloaded from the 
Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs). 
Each AOR is an individual Spitzer observation sequence, and
includes a number of data frames (the individual exposures) and the calibration data.
The data frames were selected to be 
corrected Basic Calibrated Data (cBCD), produced by the IRAC Level 1 pipeline. 
This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
and performs dark subtraction, flatfielding correction and flux calibration (into units of $\rm MJy~sr^{-1}$). 
The final product (the BCD) is a flux-calibrated image which has had all the well-understood instrumental signatures removed.
BCD frames are further processed through an ``artifact correction'' pipeline 
that mitigates the commonly found artifacts of stray light, saturation, ``muxbleed'' and column pulldown\footnote{Stray light 
includes scattered light from stars outside the array location as well as filter ghosts from bright stars. 
Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
It appears as a decaying trail of pixels, repeating every fourth column.
``Column pulldown'' is caused by a bright pixel that triggers a bias shift within its respective column, 
creating a lower background value throughout the entire column than in the surrounding columns.}.
After the artifact correction has been applied, the BCD becomes a cBCD.

@@

\subsubsection{Sky subtraction}
Sky subtraction was performed manually on the image mosaics using the tasks {\tt marksky} and {\tt skyfit} 
of the IRAF\footnote{IRAF is the Image Reduction and Analysis Facility, 
distributed by the National Optical Astronomy Observatory, 
which is operated by the Association of Universities for Research in Astronomy (AURA) 
under cooperative agreement with the National Science Foundation.} 
package GALPHOT\footnote{GALPHOT was developed in the IRAF - STSDAS environment mainly by 
W. Freudling, J. Salzer, and M. P. Haynes \citep{haynes1999galphot}.}.
The task {\tt skyfit} also provided an estimate of the sky root mean square ($RMS_{\rm sky}$).

@@

\subsubsection{1D PSF}
A universal\footnote{Across all mosaics, the variation of the Moffat $FWHM$ is $\pm 0''.1$, 
and the variation of the Moffat $\beta$ is $\pm 2.0$.
The use of a universal PSF is justified for the following reasons: 
\emph{i}) the PSF-convolution is more sensitive to the value of the $FWHM$ than $\beta$, 
i.e. having a 50\% variation in $\beta$ is not an issue as long as the variation in $FWHM$ is small;
\emph{ii}) the use of a non-signal-to-noise-weighted fitting scheme minimizes biases from a non-accurate PSF description;
\emph{iii}) not all mosaics have enough stars suitable for the PSF characterization: 
rather than having an individual PSF for each mosaic (which would have been based on only 1-2 stars for some mosaics), 
we preferred the use of a universal PSF.}, 
average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \cite{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained 
$(\alpha, \beta) = (2''.38, 4.39)$.

@@

\section{Analysis}
\label{sec:anal}
\subsection{Isophotal analysis}
We performed an isophotal analysis of our galaxies using the IRAF task {\tt ellipse} \citep{taskellipse}, 
which fits elliptical isophotes to galaxy images.
The center of the isophotes was held fixed, while the ellipticity ($\epsilon$), the position angle ($P.A.$),  
and the amplitude of the fourth harmonic\footnote{The amplitude of the fourth harmonic deviations from perfect ellipses 
($B4$) parameterizes the diskyness ($B4>0$) or boxyness ($B4<0$) of the isophotes.} ($B4$) were allowed to vary with radius.
The step in semi-major axis length between successive ellipses was first set to increase linearly, 
and then geometrically in our second run\footnote{In the case of linear steps, 
the semi-major axis length for the next ellipse was calculated by adding $1$ pixel to the current length.
In the case of geometric steps, the semi-major axis length for the next ellipse 
was calculated as $1.1$ times the current length.}.
As a result, for each galaxy we produced respectively a ``linearly sampled'' and a ``logarithmically sampled'' 
surface brightness profile along the major-axis. 
Major-axis surface brightness profiles were additionally converted into the equivalent-axis,
i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$), 
equivalent to the circularized radius.
This resulted in 4 profiles per galaxy.
Isophotes corresponding to an intensity less than 
three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$) were ignored.
Some surface brightness profiles were truncated at our discretion before the $3 \times RMS_{\rm sky}$ limit, 
according to specific technical reasons (e.g.~contamination from light of a neighboring galaxy, 
disturbed morphology in the galaxy outskirts, etc.). 
In particular, we did not attempt to fit bends or truncations of large-scale disks 
(e.g.~\citealt{erwin2005,erwin2008,erwin2012,gutierrez2011,comeron2012,munozmateos2013,kim2014}) 
but instead truncated the surface brightness profiles before the occurrence of such features. 
Individual cases are discussed in Section \ref{sec:indgal}.

@@

\subsection{1D fitting routine}
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
This software can fit an observed surface brightness profile with any linear combination of 
a set of analytical functions (S\'ersic, exponential, Gaussian, Moffat, Ferrer, symmetric Gaussian ring etc. 
see Appendix \ref{sec:app1} for a description of the analytical form of these profiles).
At each iteration, 
the model is numerically convolved with a Moffat filter, to account for PSF effects, 
and then matched to the data.
The minimization routine is based on the Levenberg-Marquardt algorithm.
During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
surface brightness profile, 
although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
The all too often over-looked flaw with (signal-to-noise)-based weighting schemes 
is that they immediately become biased weighting schemes when additional components are present but not modelled.
For example, fitting only a S\'ersic model to what is actually a nucleated elliptical galaxy immediately voids 
a (signal-to-noise)-based weighting scheme 
and results in S\'ersic parameters which describe the spheroid less accurately than had no (signal-to-noise)-weighting been used.
While we have paid careful attention to the components in each galaxy, 
this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
Over-looked partially depleted cores, or an incorrect PSF, can of course also result in (signal-to-noise)-weighted fitting schemes 
performing poorly because of the emphasis they place on matching the model to the inner data.

@@

As stressed in Section \ref{sec:int}, our investigation is primarily focused on the central spheroidal components 

@@

We modeled spheroids/bulges with a S\'ersic profile, without attempting to distinguish between classical and pseudo-bulges.  \\

@@

\cite{savorgnangraham2015ellicular} extensively discuss the topic of galaxies with intermediate-scale disks 

@@

which makes these galaxies falsely appear as extreme outliers in the (black hole mass)-(spheroid stellar mass) diagram.  \\

@@

As noted, we were able to successfully fit bars with a Ferrer function 

@@

in a few cases, with a Ferrer function\footnote{One advantage of choosing a Ferrer function over a S\'ersic profile 

@@

as is commonly found for bars in ``early-type spiral'' galaxies \citep{gadottidesouza2006}.  \\

@@

(\citealt{wadadekar1999,ravindranath2001,peng2002} and \citealt{gadotti2008} discuss the importance of fitting nuclear components). \\

@@

\subsection{2D fits}
\label{sec:2d}
Two-dimensional decompositions were carried out using the software \textsc{Imfit} \citep{imfit}.
For each galaxy, we built a 2D model that was consistent with the corresponding 1D model in terms of number and type of components. 
The only difference between our 1D and 2D models pertains to the description of bars: 
because the Ferrer profile is not made available in \textsc{Imfit},
bars were fit with a 2D Gaussian function.  \\
The 2D decomposition of NGC 2974 is presented in Figure \ref{fig:n29742d}. 
The galaxy was modeled with a S\'ersic bulge, an exponential disk and a Gaussian bar.
The nuclear component was masked and the ring was not 
modeled\footnote{We built the 2D model first including and then omitting a gaussian ring component, 
but both models converged to the same solution, i.e.~the fit ``ignored'' the presence of the faint ring. 
This did not happen in the 1D decomposition because of the different weighting scheme used by the fitting routines.}. 
Our best-fit 2D model returns a bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 10.5~\rm arcsec$, 
a bulge S\'ersic index $n_{\rm sph} = 1.3$ and a $3.6~\rm \mu m$ bulge apparent magnitude $m_{\rm sph} = 8.39~\rm mag$, 
in fairly good agreement with our 1D decomposition. 
Fits and descriptions for the other galaxies are available online.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{n2974_imgmsk.eps}
\includegraphics[width=\columnwidth]{n2974_unsharp.eps}
\includegraphics[width=\columnwidth]{n2974_model.eps}
\includegraphics[width=\columnwidth]{n2974_resid.eps}
\caption{Image of the galaxy NGC 2974 with its mask (top panel, on a logarithmic scale), 
unsharp mask (second panel, on a linear scale), 
best-fit 2D model (third panel, on a logarithmic scale), 
and residual image after the subtraction of the 2D model (bottom panel, on a linear scale; 
the residual patterns correspond to differences between the data and the model of less than 6\%).
The lefthand side of the mosaic allowed an accurate determination of the sky background level.}
\label{fig:n29742d}
\end{center}
\end{figure}

@@

\subsection{1D versus 2D decompositions}
Here we explore how 1D and 2D decompositions compare with each other. 
Readers not interested in our practical knowledge, 
having dealt with 1D and 2D techniques of galaxy modeling at the same time, can skip to Section \ref{sec:err}. 
We summarize our experience in the following points:
\begin{itemize}
\item A visual inspection of galaxy images and their unsharp masks is often not sufficient to accurately identify all of a galaxy's components. 
Weak bars and some embedded disks can easily be missed. 
Other (inclined) embedded disks can be confused with large-scale disks.
In this regards, the 1D isophotal analysis is extremely helpful. 
Local minima/maxima or abrupt changes in the ellipticity, position angle and fourth harmonic profiles contain precious information 
about a galaxy's constituents.
\item The ellipticity and position angle of triaxial spheroids can vary with radius.
The analytic functions used by 2D decomposition codes to fit galaxy components have fixed ellipticity and position angle, 
thus they cannot account for these radial gradients. 
This problem is overcome with 1D decomposition techniques 
because the ellipticity, and additionally the deviations from elliptical isophotes, 
are efficiently included in the equivalent-axis fit (see the Appendix of \citealt{ciambur2015}).
\item The interpretation of the residual surface brightness profile is often crucial to identify the optimal decomposition for a galaxy. 
In our experience, we found that interpreting 1D residuals was easier and more productive than 2D residuals.
\end{itemize}
Although we attempted 2D modeling for the 72 galaxies in our sample, 
more than half of the 2D decompositions were not successful or did not converge to a meaningful solution. 
This should serve as a tip to users of 2D fitting codes. 
When physically meaningful spheroid parameters are required, 
the output may not be reliable and should be inspected.
For the 31 galaxies that had successful 2D decompositions, 
we compare with their 1D parameters in Figures \ref{fig:re1d2d}, \ref{fig:n1d2d} and \ref{fig:mag1d2d}.
The agreement between 1D and 2D effective radii and magnitudes is remarkable, 
whereas a larger amount of scatter in the S\'ersic indices can be caused by the fact that 
2D measurements do not exactly correspond to 1D equivalent-axis measurements. 
No systematic effects are observed in any of these three plots, 
which indicates that 1D and 2D techniques of galaxy modeling -- when performed on the same galaxy -- 
can give consistent results. \\
In conclusion, since we found that the best-fit parameters do not depend on the decomposition method (1D or 2D) used, 
and given that we obtained more successful 1D decompositions than 2D, 
we will base our analysis on the results from the 1D fits.

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{comparison_n.eps} 
\caption{2D measurements of the spheroid S\'ersic indices roughly approximate the 1D equivalent-axis measurements. 
The dashed line displays the 1:1 relation.
The four most obvious outliers are NGC 821, NGC 3377, NGC 4945, and NGC 5576. 
Their individual cases are discussed in the Appendix. }
\label{fig:n1d2d}
\end{center}
\end{figure}

@@

When we identified, 
but were not able to model a galaxy sub-component with the same accuracy dedicated to the other components.

@@

\subsubsection{Uncertainties on $n_{\rm sph}$}
In Figure \ref{fig:compn}, for 58 galaxies, 
we compare the measurements of the spheroid S\'ersic index obtained by different authors 
with those obtained by us. 
For each galaxy, we computed the average value $\langle \log(n_{\rm sph}) \rangle$ of the available measurements, 
and we plot it against the scatter of the individual measurements around each spheroid's $\langle \log(n_{\rm sph}) \rangle$.
The measurements are heterogeneous, 
in the sense that they were obtained from 1D or 2D decompositions of data in different wavelengths, 
and they refer either to the major-axis, the equivalent-axis or some 2D average.
In Figure \ref{fig:compn}, the black histogram shows the distribution of the scatter around $\langle \log(n_{\rm sph}) \rangle$ 
for our measurements. 
38\% of this distribution lie within $-\sigma_1^- = -0.08~\rm dex$ and $+\sigma_1^+ = +0.06~\rm dex$, 
78\% lie within $-\sigma_2^- = -0.21~\rm dex$ and $+\sigma_2^+ = +0.17~\rm dex$,
and 92\% lie within $-\sigma_3^- = -0.25~\rm dex$ and $+\sigma_3^+ = +0.25~\rm dex$. 
We elect to use $\pm \sigma_1^\pm$, $\pm \sigma_2^\pm$ and $\pm \sigma_3^\pm$ as $1\sigma$ uncertainties 
for our measurements of $\log(n_{\rm sph})$ obtained from ``grade 1'', ``grade 2'' and ``grade 3'' fits, respectively. 
This means that, if the fit to a galaxy was classified as ``grade 1'', 
the (logarithmic) value of the spheroid S\'ersic index $\tilde{n}_{\rm sph}$ and associated uncertainties would be 
$\log(\tilde{n}_{\rm sph})^{+\sigma_1^+}_{-\sigma_1^-} = \log(\tilde{n}_{\rm sph})^{+0.06}_{-0.08}$; 
if the fit to that galaxy was classified as ``grade 2'', 
then one would have $\log(\tilde{n}_{\rm sph})^{+\sigma_2^+}_{-\sigma_2^-} = \log(\tilde{n}_{\rm sph})^{+0.17}_{-0.21}$, 
and so on.

@@

  \begin{figure}[h]
  \begin{center}
  \includegraphics[width=\fitfigurewidth]{m104_1Dfit.eps}
  \caption{M104: 
  A lenticular/spiral galaxy with a partially depleted core \citep{jardel2011}. 
  The data within the innermost $6''.1$ are excluded from the fit, 
  and the most obvious elongated feature of this galaxy is modeled with a Ferrer function. 
  The ellipticity profile indicates that the disk is of intermediate-scale 
  (for a thorough analysis of this galaxy, see \citealt{gadottisanchezjanssen2012}).
  }
  \end{center}
  \end{figure}
